Predicting sales of newly published books

### 2015-10-19 paper.tex
working in the results section (updating tables)

% con ReliefFAttributeEval salen seleccionadas (9):
% print_run num_reprints tot_points_sale tot_points_sale_1st_year reprints distrib_novelty weeks_sale + total_sales
Using the ReliefFAttributeEval feature selection method, and taking into account 
the best ranked atributes, the following variables have been selected: 
\emph{print-run, number of reprints, total points of sale, total points of sale 1st year, reprints, units distributed as novelty, weeks for sale, total sales}.

@@

% datasets:
%  original (all vars)
%  4 vars
%  9 vars
%  SOM selected vars

Table \ref{tabla:results13} shows obtained results (time to build the model and 
error) after applying the proposed forecasting methods on the dataset with 13 
variables per book.
In this dataset, every book is described using numerical variables, and thus, 
processing the data to build the different models is a fast task despite the 
number of instances.

% Mean absolute error MAE / Root mean squared error RMSE /  Relative absolute error RAE / Root relative squared error RRSE
  % ¿Qué sentido tiene usar los 4 métodos de error? ¿Es que vamos a seleccionar uno? - JJ
  %[pedro] es lo habitual en los trabajos en los que se realizan tareas de predicción
  % en algunos calculan muchos más, pero estos son los más usados. 
\begin{table*}[!h]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
 Method 	& Time (sec.) 	      & MAE 		& RMSE 		& RAE (\%) & RRSE (\%) 		\\
\hline
  M5P 		& 2.94 $\pm$ 0.51 	  & 65.49 	& 133.73 	& 11.10 	 & 9.17 	  \\
\hline
  LR 		  & 0.33 $\pm$ 0.07 	  & 100.813 & 257.63 	& 17.09 	 & 17.67 	\\
\hline
  SVM 		& 49.10 $\pm$ 8.05	  & 52.30	  & 139.45	& 8.87     & 9.56  	\\
\hline
  kNN 		& 0.03 $\pm$ 0.01 	  & 198.16 	& 542.93 	& 33.59 	 & 37.24 	\\
\hline
  MLP 		& 12.70 $\pm$ 3.08 	  & 97.18 $\pm$ 24.74 	& 174.77 $\pm$ 31.50 	& 16.47 $\pm$ 4.19 	& 11.99 $\pm$ 2.16 	\\
\hline
\end{tabular}
\end{center}
\caption{\small{Results (errors and time) obtained using the different
    forecasting methods on the dataset with 13 variables per book.}} 
\label{tabla:results13}
\end{table*}

Obtained results (time to build the model and error) using the different 
forecasting methods on the dataset with 7 variables per book can be shown 
in Table \ref{tabla:results7}.
Although in this dataset each book is described using a smaller number of 
variables, two categorical variables, \emph{EDITORIAL} and \emph{SUBJECT}, are 
included, what that makes harder to process the instances and build the different 
models.

  %[pedro] ya están todos los resultados de de tabla:results7 (MP5, LR, KNN, SVM, MLP)
\begin{table*}[!h]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
 Method   & Time (sec.)         & MAE     & RMSE    & RAE (\%)  & RRSE (\%)      \\
\hline
  M5P     & 7.77 $\pm$ 1.15     & 117.78  & 260.05  & 18.51     & 17.00  \\
\hline
  LR      & 41.72 $\pm$ 8.41    & 120.29  & 252.91  & 18.91     & 16.54   \\
\hline
  SVM     & 1652.20 $\pm$ 283.50& 109.30  & 251.16   & 17.18    & 16.42   \\
\hline
  kNN     & 0.03 $\pm$ 0.01     & 293.98  & 1071.52  & 46.21    & 70.06   \\
\hline
  MLP     & 3643.59 $\pm$ 72.40 & 696.92 $\pm$ 85.38 & 1609.37 $\pm$ 76.44  & 108.54 $\pm$ 13.34  & 105.96 $\pm$ 4.93   \\
\hline
\end{tabular}
\end{center}
\caption{\small{Results (errors and time) obtained using the different 
forecasting methods on the dataset with 7 variables per book.}}
\label{tabla:results7} %FERGU: es normal que con menos variables tarde más? Sí, el uso de MATERIA y EDITORIAL hacen que el conjunto sea endiablado.
\end{table*}

>>>>

% con ReliefFAttributeEval salen seleccionadas (9):
% print_run num_reprints tot_points_sale tot_points_sale_1st_year reprints distrib_novelty weeks_sale + total_sales
Using the ReliefFAttributeEval feature selection method, and taking into account 
the best ranked atributes, the following variables have been selected: 
\emph{print-run, number of reprints, total points of sale, total points of sale 
first year, reprints, units distributed as novelty, weeks for sale, total sales}.

@@

% datasets:
%  original (16 vars)
%  4 vars
%  9 vars
%  SOM selected vars

Table \ref{tabla:resultsT} shows obtained results (time to build the model and 
error) after applying the proposed forecasting methods on the original dataset,
using the 16 available variables per book.
In this dataset, every book is described using not only numerical variables, 
but using two additional categorical variables, \emph{editorial} and \emph{collection}, 
what makes harder to process the instances and build the different models.

% Mean absolute error MAE / Root mean squared error RMSE /  Relative absolute error RAE / Root relative squared error RRSE
  % ¿Qué sentido tiene usar los 4 métodos de error? ¿Es que vamos a seleccionar uno? - JJ
  %[pedro] es lo habitual en los trabajos en los que se realizan tareas de predicción
  % en algunos calculan muchos más, pero estos son los más usados. 
\begin{table*}[!h]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
 Method 	& Time (sec.) 	      & MAE 		& RMSE 		& RAE (\%) & RRSE (\%) 		\\
\hline
  M5P 		& 2.94 $\pm$ 0.51 	  & 65.49 	& 133.73 	& 11.10 	 & 9.17 	  \\
\hline
  LR 		  & 0.33 $\pm$ 0.07 	  & 100.813 & 257.63 	& 17.09 	 & 17.67 	\\
\hline
  SVM 		& 49.10 $\pm$ 8.05	  & 52.30	  & 139.45	& 8.87     & 9.56  	\\
\hline
  kNN 		& 0.03 $\pm$ 0.01 	  & 198.16 	& 542.93 	& 33.59 	 & 37.24 	\\
\hline
  MLP 		& 12.70 $\pm$ 3.08 	  & 97.18 $\pm$ 24.74 	& 174.77 $\pm$ 31.50 	& 16.47 $\pm$ 4.19 	& 11.99 $\pm$ 2.16 	\\
\hline
\end{tabular}
\end{center}
\caption{\small{Results (errors and time) obtained using the different
    forecasting methods on the original dataset (16 variables per book).}} 
\label{tabla:resultsT}
\end{table*}

Obtained results (time to build the model and error) using the different 
forecasting methods on the dataset with 9 variables per book (obtained 
using the ReliefFAttributeEval feature selection method) can be shown 
in Table \ref{tabla:results9}.
In this dataset, every book is described using numerical variables, and thus, 
processing the data to build the different models is a fast task.

\begin{table*}[!h]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
 Method   & Time (sec.)         & MAE     & RMSE    & RAE (\%)  & RRSE (\%)      \\
\hline
  M5P     & 7.77 $\pm$ 1.15     & 117.78  & 260.05  & 18.51     & 17.00  \\
\hline
  LR      & 41.72 $\pm$ 8.41    & 120.29  & 252.91  & 18.91     & 16.54   \\
\hline
  SVM     & 1652.20 $\pm$ 283.50& 109.30  & 251.16   & 17.18    & 16.42   \\
\hline
  kNN     & 0.03 $\pm$ 0.01     & 293.98  & 1071.52  & 46.21    & 70.06   \\
\hline
  MLP     & 3643.59 $\pm$ 72.40 & 696.92 $\pm$ 85.38 & 1609.37 $\pm$ 76.44  & 108.54 $\pm$ 13.34  & 105.96 $\pm$ 4.93   \\
\hline
\end{tabular}
\end{center}
\caption{\small{Results (errors and time) obtained using the different 
forecasting methods on the dataset with 9 variables per book.}}
\label{tabla:results9}
\end{table*}

Finally, obtained results (time to build the model and error) using the different 
forecasting methods on the dataset with 4 variables per book (obtained 
using the CfsSubsetEval feature selection method) can be shown 
in Table \ref{tabla:results4}.
As in the previous case, in this dataset every book is described using numerical 
variables. Thus, due to the number of features per book, building the different 
models is faster than in the previous cases.

\begin{table*}[!h]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
 Method   & Time (sec.)         & MAE     & RMSE    & RAE (\%)  & RRSE (\%)      \\
\hline
  M5P     & 7.77 $\pm$ 1.15     & 117.78  & 260.05  & 18.51     & 17.00  \\
\hline
  LR      & 41.72 $\pm$ 8.41    & 120.29  & 252.91  & 18.91     & 16.54   \\
\hline
  SVM     & 1652.20 $\pm$ 283.50& 109.30  & 251.16   & 17.18    & 16.42   \\
\hline
  kNN     & 0.03 $\pm$ 0.01     & 293.98  & 1071.52  & 46.21    & 70.06   \\
\hline
  MLP     & 3643.59 $\pm$ 72.40 & 696.92 $\pm$ 85.38 & 1609.37 $\pm$ 76.44  & 108.54 $\pm$ 13.34  & 105.96 $\pm$ 4.93   \\
\hline
\end{tabular}
\end{center}
\caption{\small{Results (errors and time) obtained using the different 
forecasting methods on the dataset with 4 variables per book.}}
\label{tabla:results4}
\end{table*}
